Stack Safety is a Security Property

### 2021-04-14 tex/main.tex
Comments

For the sake of concreteness, most of our presentation assumes a RISC-V
machine architecture with a basic subroutine calling convention (passing
parameters in registers) and a micropolicy-like enforcement mechanism. We
also show how to accomodate stack-allocated parameter passing and
coroutines.

\bcp{this is also a
  good place to admit that our definitions are tuned for micropolicies, if
  we can find a succinct way to say it.}
\sna{See above.}
\bcp{I added it to the last paragraph (which is pretty close to the preceding
  paragraph :-)  We should follow this up with some discussion in the (new)
  Assumptions section about how different enforcement mechanisms (us,
  StkTokens, maybe others) adopt different perspectives on what the stack is
for and how it is organized and so lead to somewhat different notions of
low-level safety.}

@@

\bcp{This paragraph doesn't apply to the lazy properties, so maybe it should
be moved before they are introduced?}%
To illustrate the applicability of these properties, we perform randomized testing to
validate that \citeauthor{DBLP:conf/sp/RoesslerD18}'s Depth Isolation micro-policy enforces
them. Randomized testing is a relatively low-cost way to validate a potential enforcement
mechanism; it finds flaws in the enforcement fast enough to be integrated into the workflow
of enforcement development \citep{TestingNI:ICFP}. To demonstrate that the testing adequately
covers potentially erroneous programs, we test intentionally buggy policies alongside
the real one. If the testing can differentiate correct implementations from buggy ones,
it is an argument in favor of their correctness. \bcp{Hmm--don't understand
  that sentence}
%\apt{more to say?}\bcp{Yes---partly to underscore our claim that this is a
%  significant contribution, and partly to give the reader some context for
%  why this is part of our story.  E.g., ``One nice thing we can do with our
%  spec is to use it to evaluate the claims of existing or future proposals
%  for enforcement mechanisms.  One relatively inexpensive way to carry out
%  such an evaluation is to see whether property-based testing against this
%  spec can distinguish correct implementations of the mechanism from buggy
%  ones...''}
Of course, as our testing reveals, \citeauthor{DBLP:conf/sp/RoesslerD18}'s Lazy Tagging and
Clearing micro-policy does not enforce stepwise integrity.
Unfortunately the existing Lazy Tagging and Clearing
micro-policy does not quite enforce observable confidentiality either. %, as we show in
%testing~\apt{really??},
But formalizing the ideal property allows us to see how it falls short -- a specific
violation of the temporal aspect of confidentiality.
We propose  a variant of Lazy Tagging and Clearing that we believe \emph{does} enforce
observational integrity, at some performance cost.\apt{but we're not testing that, right?}
\rb{Not sure about the property part right now, the machine side of this is
  pretty much done}
\sna{It's aspirational so far, but there's no fundamental reason we can't test it. We may
  need a caveat about how it's harder to test?}\apt{As per email discussion,
  maybe we could have a property variant that \emph{does} match depth-based Lazy Tagging and
  Clearing, by loosening the temporal safety properties?}
\sna{I'm pretty sure for the main policy it's just lazy integrity, no confidentiality.
  There was a variant Nick and Andre gave that would restrict the leaks to only be between
  instances of the same function, so that's the same property under a weaker attacker model,
  where we don't protect a function from itself.}

@@

\bcp{I would still advocate splitting this into two sections, just so the
  transition from one to the other and the division of responsibility are
  clear.  The first section could be called ``What is 'the Stack'?'' instead
of ``Assumptions'' if we want.}

@@

Our properties are defined in terms of an abstract machine model that makes very few
assumptions about the concrete machine that instantiates it.  We assume a register
machine with a program counter \(\PCname\); other
details of the machine's ISA are unimportant. We assume that we know ahead of time
the layout of memory, including where code lives and which addresses are within
the bounds of the stack.

@@

Alternatively, an annotated instruction might not really be a call or return.
In the context of \citeauthor{DBLP:conf/sp/RoesslerD18}'s micro-policies, well-behaved calls
and returns are implemented by fixed sequences of instructions which the tag policy
will force to be executed from start to finish. The annotated call or return instruction should always
be the final instruction of the appropriate sequence. What if an annotated instruction exists outside
such a sequence? We will statically rule out some scenarios with a well-formedness criterion
on initial states: annotated instructions will initially be tagged apropriately, as the
final instruction in the call or return sequence, and all blessed sequences will end with
annotated instructions. This is all we need for the policy to
protect itself: it can then failstop if it would execute the blessed sequence out of order.
So, even in our strong attacker model, we need very little in the way of restrictions on
the code when considering micropolicy-based enforcement.

@@

\section{Demonstrating Stack Safety}
\label{sec:running-example}
\colorlet{lgray}{gray!40}
\colorlet{lred}{red!40}
\colorlet{lblue}{blue!20}

>>>>

For the sake of concreteness, most of our presentation assumes a standard RISC
machine architecture with a basic subroutine calling convention (parameters
passed in registers) and a micropolicy-like enforcement mechanism. We
also show how to accomodate stack-allocated parameter passing and
coroutines.

\bcp{this is also a
  good place to admit that our definitions are tuned for micropolicies, if
  we can find a succinct way to say it.}
\sna{See above.}
\BCP{I added it to the last paragraph (which is pretty close to the preceding
  paragraph :-)  We should follow this up with some discussion in the (new)
  Assumptions section about how different enforcement mechanisms (us,
  StkTokens, maybe others) adopt different perspectives on what the stack is
for and how it is organized and so lead to somewhat different notions of
low-level safety.}

@@

\BCP{This paragraph doesn't apply to the lazy properties, so maybe it should
be moved before they are introduced?}%
To illustrate the applicability of these properties, we perform randomized testing to
validate that \citeauthor{DBLP:conf/sp/RoesslerD18}'s Depth Isolation micro-policy enforces
them. Randomized testing is a relatively low-cost way to validate a potential enforcement
mechanism; it finds flaws in the enforcement fast enough to be integrated into the workflow
of enforcement development \citep{TestingNI:ICFP}. To demonstrate that the testing adequately
covers potentially erroneous programs, we test intentionally buggy policies alongside
the real one. If the testing can differentiate correct implementations from buggy ones,
it is an argument in favor of their correctness. \bcp{Hmm--don't understand
  that sentence}
%\apt{more to say?}\bcp{Yes---partly to underscore our claim that this is a
%  significant contribution, and partly to give the reader some context for
%  why this is part of our story.  E.g., ``One nice thing we can do with our
%  spec is to use it to evaluate the claims of existing or future proposals
%  for enforcement mechanisms.  One relatively inexpensive way to carry out
%  such an evaluation is to see whether property-based testing against this
%  spec can distinguish correct implementations of the mechanism from buggy
%  ones...''}
Of course, as our testing reveals, \citeauthor{DBLP:conf/sp/RoesslerD18}'s Lazy Tagging and
Clearing micro-policy does not enforce stepwise integrity.
Unfortunately the existing Lazy Tagging and Clearing
micro-policy does not quite enforce observable confidentiality either. %, as we show in
%testing~\apt{really??},
But formalizing the ideal property allows us to see how it falls short -- a specific
violation of the temporal aspect of confidentiality.
We propose  a variant of Lazy Tagging and Clearing that we believe \emph{does} enforce
observational integrity, at some performance cost.\apt{but we're not testing that, right?}
\rb{Not sure about the property part right now, the machine side of this is
  pretty much done}
\sna{It's aspirational so far, but there's no fundamental reason we can't test it. We may
  need a caveat about how it's harder to test?}\apt{As per email discussion,
  maybe we could have a property variant that \emph{does} match depth-based Lazy Tagging and
  Clearing, by loosening the temporal safety properties?}
\sna{I'm pretty sure for the main policy it's just lazy integrity, no confidentiality.
  There was a variant Nick and Andre gave that would restrict the leaks to only be between
  instances of the same function, so that's the same property under a weaker attacker model,
  where we don't protect a function from itself.}

@@

\BCP{I would still advocate splitting this into two sections, just so the
  transition from one to the other and the division of responsibility are
  clear.  The first section could be called ``Setup'' or something like
  that.}

@@

Our properties are defined in terms of an abstract machine model that makes very few
assumptions about the concrete machine that instantiates it.  We assume a register
machine with a program counter \(\PCname\); other
details of the machine's ISA are unimportant. We assume that we know ahead of time
the layout of memory, including where code lives and which addresses are within
the bounds of the stack.  \BCP{What should we say about the heap?}

@@

Alternatively, an annotated instruction might not really be a call or return.
In the context of \citeauthor{DBLP:conf/sp/RoesslerD18}'s micro-policies, well-behaved calls
and returns are implemented by fixed sequences of instructions which the tag policy
will force to be executed from start to finish. The annotated call or return instruction should always
be the final instruction of the appropriate sequence. What if an annotated instruction exists outside
such a sequence? We will statically rule out some scenarios with a well-formedness criterion
on initial states: annotated instructions will initially be tagged apropriately, as the
final instruction in the call or return sequence, and all blessed sequences will end with
annotated instructions. This is all we need for the policy to
protect itself: it can then failstop if it would execute the blessed sequence out of order.
So, even in our strong attacker model, we need very little in the way of restrictions on
the code when considering micropolicy-based enforcement.  \BCP{Is this
  discussion still needed?  I had hoped that switching to our ``new''
  definition on subtraces would eliminate such complexities!}

@@

\section{Key Ideas}
\label{sec:running-example}
\colorlet{lgray}{gray!40}
\colorlet{lred}{red!40}
\colorlet{lblue}{blue!20}
